### 2025-01-15 paper/icml25/first/sects/background.tex
minors + last related para

>>>>

For simplicity, we formally treat only the case where the policy observe the full state to make the action. However, in our experiments, we consider also scenarios where the full state is not available to the policy. In such cases, the MDP includes a set of observations, $\mathcal{O}$, an observation function $O:\mathcal{S}\rightarrow\mathcal{O}$, and the policy is a function $\pi:\mathcal{O}\rightarrow\mathcal{A}$. In such cases, the MDP takes the name of Partially Observable Markov Decision Process (POMDP).

### 2025-01-15 paper/icml25/first/sects/related.tex
minors + last related para

\paragraph{Reinforcement Learning on Differentiable Engines}

>>>>

\paragraph{Reinforcement Learning on Differentiable Engines}
Precursors of SHAC with similar intuition are PODS~\cite{Mora21} and CE-APG~\cite{Gillen22}. In \cite{Lv23}, the authors introduce rendering to enhance model-based RL. \cite{Zheng24} employes a differentiable symbolic expression search engine. Trajectory optimization approach is taken in \cite{Wan24}. \cite{Georgiev24} takles unstable gradient due to stiff dynamics by adaptively truncating trajectories when these occur. With respect to this approach, we take a substantially different method, by emulating the differentiable environment with a trained neural network.
